---
title: "Matching overview"
date: "16. Januar 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(error = TRUE, echo=FALSE, cache=FALSE)
library(ggplot2)
library(SeminarMatching)
library(dplyr)
library(tidyr)
```

```{r init_param, include=FALSE}
semester = "SS15"
db.dir = paste0("../db")
```

```{r load_data, include=FALSE}
semdb = dbConnect(dbname=paste0(db.dir,"/semDB.sqlite"), drv = SQLite())
matchings = dbGet(semdb,"matchings",nlist(semester))
seminars = dbGet(semdb,"seminars",nlist(semester))
students = dbGet(semdb,"students",nlist(semester))
```

```{r init_data, include=FALSE}
df = matchings
df = mutate(df, found=ifelse(semid!=-1, "found seminar", "no seminar"))

cols = c("semid",setdiff(colnames(seminars),colnames(df)))
df = left_join(df, seminars[,cols,drop=FALSE], by="semid")

cols = c("userid",setdiff(colnames(students),colnames(df)))
df = left_join(df, students[,cols,drop=FALSE], by="userid")

num.studs = length(unique(df$userid))
num.sems = length(unique(df$semid))
num.match = sum(df$semid != -1)
num.empty = sum(df$semid == -1)
total.slots = sum(seminars$slots)
```



- We have `r num.studs` students and `r num.sems` seminars.

- `r num.match` of `r total.slots` seminar slots have been filled (`r round(100*num.match / total.slots)`%) and `r num.empty` students (`r round(100*num.empty / num.studs)`%) did not get assigned a seminar.

- On average a student listed `r round(mean(df$num_ranked),1)` seminars in the preference list.

```{r results="asis"}
sdf = df %>%
  group_by(studBAMA,found) %>% 
  summarise(n=n()) %>%
  ungroup() %>%
  spread(key = found, value=n) %>%
  as.data.frame()

sdf$total = sdf[,2]+sdf[,3]
knitr::kable(sdf)
```

Here are the shares of **Bachelor** students that got the seminar that they ranked at n'th position... 

```{r results='asis'}
sdf = df %>% 
  filter(studBAMA=="Bachelor") %>%
  mutate(N=n()) %>%
  group_by(studBAMA,pos, found) %>% 
  summarise(share = paste0(round(100*n() / first(N),1),"%")) %>%
  ungroup() %>%
  mutate(pos = paste0("Ranked ",pos)) %>%
  spread(key = pos, value=share)


knitr::kable(sdf)
```

and here the same for **Master** students...

```{r results='asis'}
sdf = df %>% 
  filter(studBAMA=="Master") %>%
  mutate(N=n()) %>%
  group_by(studBAMA,pos, found) %>% 
  summarise(share = paste0(round(100*n() / first(N),1),"%")) %>%
  ungroup() %>%
  mutate(pos = paste0("Ranked ",pos)) %>%
  spread(key = pos, value=share)

knitr::kable(sdf)
```

In an ideal world for students, every student gets his first ranked seminar. The rows where found equals `no seminar` describe the share of students who did not get a seminar and have ranked one seminar less than the rank column (i.e. the option `no seminar` is ranked as the rank column indicates). If students have ranked only very few seminars it may not be surprising that they did not get a seminar. It is not so good if students who have ranked a lot of seminars still do not get a seminar.

Let us show it graphically

```{r results='asis', width=11}
sdf = df %>% 
  group_by(studBAMA) %>%
  mutate(N=n()) %>%
  group_by(studBAMA,pos, found) %>% 
  summarise(share = round(100*n() / first(N),1))

ggplot(sdf, aes(share,x=pos, fill=found)) + 
  geom_bar(stat = "identity") +
  facet_wrap(~studBAMA)+
  ggtitle("Share of students that got their n'th ranked seminar (or no seminar)")
```


And now we show how the length of a students' preference lists relates with the share of students that got assigned a seminar:
```{r}
sdf = df %>% 
  group_by(studBAMA,num_ranked) %>% 
  mutate(N=n()) %>%
  group_by(studBAMA,num_ranked, found) %>% 
  summarise(share = round(100*n() / first(N),1))


ggplot(sdf, aes(share,x=found, fill=found)) + 
  geom_bar(stat = "identity") +
  facet_grid(studBAMA~num_ranked)+
  ggtitle("Share of students that got seminar depending on length of preference list")
```


Let us now graphically compare for Bachelor students the seminar matching by their main subject:

```{r}
library(ggplot2)
sdf = df %>% filter(studBAMA=="Bachelor") %>% group_by(studSubject, found) %>% summarise(n=n()) 

ggplot(sdf, aes(y=n,x=found, fill=found)) + 
  facet_wrap(~studSubject)+
  geom_bar(stat = "identity") +
  ggtitle("Bachelor: Assigned Seminars by first Subject")
```

and the same thing for master students...
```{r}
library(ggplot2)
sdf = df %>% filter(studBAMA=="Master") %>% group_by(studSubject, found) %>% summarise(n=n()) 

ggplot(sdf, aes(y=n,x=found, fill=found)) + 
  geom_bar(stat = "identity") +
  facet_wrap(~studSubject)+
  ggtitle("Master: Assigned Seminars by first subject")

```

