
```{r setup, include=FALSE}
knitr::opts_chunk$set(error = TRUE, echo=FALSE, cache=FALSE)
library(ggplot2)
library(SeminarMatching)
library(dplyr)
library(tidyr)
library(reshape2)
```

```{r init_param, include=FALSE}
setwd("D:/libraries/SeminarMatching/semapps/shared/reports")
semester = "SS16"
db.dir = paste0("../db")
round = 1
semid = 3
semdb = dbConnect(dbname=paste0(db.dir,"/semDB.sqlite"), drv = SQLite())
```

```{r init_data, include=FALSE}
matchings = dbGet(semdb,"matchings",nlist(semester, round, semid))
seminars = dbGet(semdb,"seminars",nlist(semester, semid))
studpref = dbGet(semdb,"studpref",nlist(semester, semid))
students = dbGet(semdb,"students",nlist(semester))

df = studpref
cols = c("semid",setdiff(colnames(seminars),colnames(df)))
df = left_join(df, seminars[,cols,drop=FALSE], by="semid")
cols = c("userid",setdiff(colnames(students),colnames(df)))
df = left_join(df, students[,cols,drop=FALSE], by="userid")
cols = c("semid","userid",setdiff(colnames(matchings),colnames(df)))
df = left_join(df, matchings[,cols,drop=FALSE], by=c("semid","userid"))
df$matched = !is.na(df$slot)

df$Matched = ifelse(df$matched, "matched","not")
seminar = as.list(seminars[1,])


num.prefs = NROW(df)
num.matched = sum(df$matched)
```

### `r seminar$name` `r semester`

This is a report for the main matching round.

- A total of `r num.prefs` students have put the seminar in their preference list.

- `r num.matched` students got one of the `r seminar$slots` slots in the main matching round.


The following table shows how many students ranked the seminar at position `pos` and how many of them were matched to the seminar or not.
```{r }
sdf = df %>%
  group_by(pos,Matched) %>% 
  summarise(n=n()) %>%
  spread(key = Matched, value=n) %>%
  replace.na(0, cols=-1) %>%
  as.data.frame()

sdf$total = rowSums(sdf[,-1],na.rm = TRUE)
sdf
```

The following table compares students that put the seminar in their preference list by their main subject.

```{r }
sdf = df %>%
  group_by(studSubject,Matched) %>% 
  summarise(n=n()) %>%
  spread(key = Matched, value=n) %>%
  replace.na(0, cols=-1) %>%
  as.data.frame()

sdf$total = rowSums(sdf[,-1],na.rm = TRUE)
sdf = arrange(sdf, -total)
sdf
```

The following table compares WiWi students that put the seminar in their preference list by their specialization (students with 2 specializations count 1/2 for each specialization):

```{r }
d = select(df,userid, Matched, studBAMA, studSpecBA, studSpecMA, studSpecMA2)
d = tidyr::gather(d,key = specid,value = spec,studSpecBA, studSpecMA, studSpecMA2)

d = filter(d, 
  (studBAMA=="Bachelor" & specid=="studSpecBA") | 
  (studBAMA=="Master" & specid=="studSpecMA") |
  (studBAMA=="Master" & specid=="studSpecMA2")
)

d = d %>% 
  group_by(userid) %>%
  mutate(weight=1/n())
  

sdf = d %>%
  group_by(spec,Matched) %>% 
  summarise(n=sum(weight)) %>%
  spread(key = Matched, value=n) %>%
  replace.na(0, cols=-1) %>%
  as.data.frame()

sdf$total = rowSums(sdf[,-1],na.rm = TRUE)
sdf = arrange(sdf, -total)
sdf
```

