
```{r setup, include=FALSE}
knitr::opts_chunk$set(error = TRUE, echo=FALSE, cache=FALSE)
library(ggplot2)
library(SeminarMatching)
library(dplyr)
library(tidyr)
library(reshape2)
```

```{r init_param, include=FALSE}
setwd("D:/libraries/SeminarMatching/semapps/shared/reports")
semester = "SS17"
db.dir = paste0("../db")
round = 1

semdb = dbConnect(dbname=paste0(db.dir,"/semDB.sqlite"), drv = SQLite())
matchings = dbGet(semdb,"matchings",nlist(semester))
seminars = dbGet(semdb,"seminars",nlist(semester))
students = dbGet(semdb,"students",nlist(semester))

studpref = dbGet(semdb,"studpref", nlist(semester))

manual = dbGet(semdb,"manual",nlist(semester))

```

```{r init_data, include=FALSE}
matchings1 = filter(matchings, round==1)

matchings2 = filter(matchings, round==2) %>%
  filter(num_ranked>0)

matchings = matchings1

df = matchings %>% filter(num_ranked>0)

df = mutate(df, found=ifelse(semid!=-1, "found seminar", "no seminar"))

cols = c("semid",setdiff(colnames(seminars),colnames(df)))
df = left_join(df, seminars[,cols,drop=FALSE], by="semid")

cols = c("userid",setdiff(colnames(students),colnames(df)))
df = left_join(df, students[,cols,drop=FALSE], by="userid")

num.studs = length(unique(df$userid))
num.sems = length(unique(df$semid))
num.match = sum(df$semid != -1)
num.empty = sum(df$semid == -1)
total.slots = sum(seminars$slots)

r1fi = df %>% 
  filter(semid>-1) %>%
  group_by(semid) %>%
  summarize(filled_round1=n())

seminars = left_join(seminars,r1fi, by="semid")

# computations for round 2
sp1 = filter(studpref, round==1)
sp2 = filter(studpref, round==2)

found1 = filter(df, round==1, semid > -1)$userid %>%
  unique()

r2_num = length(unique(sp2$userid))


r2_new = length(setdiff(unique(sp2$userid), unique(sp1$userid)))
r2_extra = length(intersect(unique(sp2$userid), unique(found1)))

# adapt manual
#man = manual %>% 
#  group_by(userid) %>%
#  summarize(net_added = # sum(added==1)-sum(added==0)) %>%
#  filter(net_added != 0)

n_man_added = sum(manual$added==1)
n_man_removed = sum(manual$added==0)

```

# Matching Results for `r semester` round `r round`

- Note: The report considers only students that have ranked at least 1 seminar.

- We have `r num.studs` students and `r num.sems` seminars.

- `r num.match` of `r total.slots` seminar slots have been filled (`r round(100*num.match / total.slots)`%) and `r num.empty` students (`r round(100*num.empty / num.studs)`%) did not get assigned a seminar.

- On average a student listed `r round(mean(df$num_ranked),1)` seminars in the preference list.

Filled and open seminar slots after matching round 1:
```{r}
seminars %>%
  group_by(semBAMA) %>%
  summarize(num_sems=n(), total_slots=sum(slots,na.rm=TRUE), filled=sum(filled_round1,na.rm=TRUE), open=total_slots-filled)

```


The following table shows for Bachelor and Master students, how many students found or found not a seminar.
```{r }
sdf = df %>%
  group_by(studBAMA,found) %>% 
  summarise(n=n()) %>%
  ungroup() %>%
  spread(key = found, value=n) %>%
  replace.na(0) %>%
  as.data.frame()

if (ncol(sdf)==2)
  sdf$not_found  = 0
  
sdf$total = sdf[,2]+sdf[,3]
sdf
```

Here are the shares of students that got the seminar that they ranked at n'th position... 
```{r }
df %>%
  filter(num_ranked >0) %>%
  group_by(studBAMA) %>%
  mutate(N=n()) %>%
  group_by(studBAMA,pos, found) %>% 
  summarise(share = paste0(round(100*n() / first(N),1),"%")) %>%
  ungroup() %>%
  filter(found == "found seminar") %>%
  dcast(pos ~ studBAMA+found, value.var="share") %>%
  mutate(pos = paste0("Ranked ",pos)) %>%
  replace.na("0%")
```

And now we show how the length of a students' preference lists relates with the share of students that got assigned a seminar:
```{r}
df %>% 
  group_by(studBAMA,num_ranked) %>% 
  mutate(N=n()) %>%
  group_by(studBAMA,num_ranked, found) %>% 
  summarise(share = paste0(round(100*n() / first(N),1),"%")) %>%
  dcast(num_ranked ~ studBAMA + found,value.var="share") %>%
  replace.na("0%")
```

Here are the number of students that rankend `num_ranked` seminars:
```{r}
df %>% 
  group_by(studBAMA,num_ranked) %>% 
  summarise(number_students=n()) %>%
  dcast(num_ranked ~ studBAMA,value.var="number_students") %>%
  replace.na(0) %>%
  mutate("Total Number of Students" = Bachelor + Master)
```


Let us now compare for Bachelor students the seminar matching by their main subject:

```{r}
df %>% 
  filter(studBAMA=="Bachelor") %>% 
  group_by(studSubject) %>%
  mutate(mean_num_sem_ranked=round(mean(num_ranked),1)) %>%
  group_by(studSubject, mean_num_sem_ranked, found) %>% 
  summarise(n=n()) %>%
  dcast(studSubject + mean_num_sem_ranked ~ found,value.var="n") %>%
  arrange(-`found seminar`) %>%
  replace.na(0)
```

and the same thing for master students...
```{r}
df %>% 
  filter(studBAMA=="Master") %>% 
  group_by(studSubject) %>%
  mutate(mean_num_sem_ranked=round(mean(num_ranked),1)) %>%
  group_by(studSubject, mean_num_sem_ranked, found) %>% 
  summarise(n=n()) %>%
  dcast(studSubject + mean_num_sem_ranked ~ found,value.var="n") %>%
  arrange(-`found seminar`) %>%
  replace.na(0)
```


# Filled slots after all matching rounds and manual assignments

```{r}
seminars %>%
  group_by(semBAMA) %>%
  summarize(num_sems=n(), total_slots=sum(slots), filled=sum(filled_slots), open=total_slots-filled)
```

# Matching round 2

- `r r2_num` students have submitted preferences in round 2.
- `r r2_num-r2_extra` of students did not get a slot in round 1. They either forgot to participate in round 1 (`r r2_new` students) or submitted a too short preference list in round 1, and now decided to accept also other seminars (`r r2_num-r2_extra-r2_new` students). Yet, chances are much lower to get a seat in round 2.

- `r r2_extra` of students already got a seminar in round 1, and probably want to take two seminars. In an ideal world without mistakes (like forgetting to participate in round 1), this would be the only reason to participate in round 2. 

- In total `r sum(matchings2$semid>=0)` of the `r r2_num` students got assigned a seminar slot in round 2.

# Manually added or removed students

- Manually `r n_man_added` students have been added, and `r n_man_removed` students have been removed from seminars.

Background:
- Because the world is not ideal, after the matching rounds, some students may drop out from the seminar, e.g. because they were dissatisfied with their topic, and then have been removed from the seminar list.
- Other students are added, either as replacement for dropped out students, or because of an expansion of slots due to high demand.
- Note that the numbers below would only be correct, if all lectures insert all additions and removals in the database and if no student would is added or removed multiple times.
